GHG model

### 2021-07-13 210617_GHG_model.Rmd
edits 13.07.21

# Manure management methane ($CH_4$) and nitrous oxide ($N_2O$)
volsol<-(gross_energy_intake*(1-(dig_energy/100))+(0.04*gross_energy_intake))*((1-0.08)/18.45) 
mm_ch4<-(volsol*365)*(bo*0.67*((mms_pasture*0.015)+(mms_spread*0.005)+(mms_drylot*0.015)+(mms_solidstore*0.04)+
        (mms_composted*0.005)+(mms_liquid*0.2)+(mms_biogas*0.1)+(mms_burn*0.1)))

# Estimate CO2eq for manure methane
mm_CO2<-mm_ch4*25*365

>>>>

# Manure management methane ($CH_4$) and nitrous oxide ($N_2O$)
# daily volatile solid excreted (page 10.42 of 2006 IPCC Guidelines for National Greenhouse Gas Inventories)

volsol<-(gross_energy_intake*
           (1-(dig_energy/100))+
           (urinary_energy*gross_energy_intake))*
             ((1-ash_content)/18.45)

# The maximum methane emission from manure (Bo) depends on the animal type. In the input table, we
# treat these as constants for each animal type. The following line assigns the corresponding Bo value
# to the Bo variable. In the dataset we're using for Kenya, only two values for Bo are given: 0.17 for
# animal types 4-6 and 0.135 for animal types 1-3 and 7-12.

Bo<-eval(parse(text=paste0("Bo_animaltype_",animal_type)))

# the following is page 10.41 of the 2006 IPCC Guidelines for National Greenhouse Gas Inventories
mm_ch4<-(volsol*365)*
        (Bo*0.67*
           ((mms_pasture*MCFpasture)+
            (mms_spread*MCFspread)+
            (mms_drylot*MCFdrylot)+
            (mms_solidstore*MCFsolidstore)+
            (mms_composted*MCFcomposted)+
            (mms_liquid*MCFliquid)+
            (mms_biogas*MCFbiogas)+
            (mms_burn*MCFburn)+
              # the original code was lacking the 'sold' fraction - we added this for completeness
            (mms_sold*MCFsold)))

# Estimate CO2eq for manure methane
### this one also contained a multiplication by 365 that seemed erroneous
mm_CO2<-mm_ch4*25

##### WE STOPPED HERE
